%!TEX ROOT=..\zpevnik.tex

Do you [C]ever like breaking down?
Do you [Am]ever feel out of place?
Like [C]somehow you just don't belong,
and [G]no one understands you.
Do you [C]ever wanna run away?
Do you [Am]lock yourself in your room?
With the [C]radio on turned up so loud,
and [G]no one hears you screaming.

®: No you don't know what its like
When [Am]nothing feels alright
You [F]don't know what its like to be like [G]me...

To be [Am]hurt, to feel [F]lost, to be [C]left out in the [G]dark
To be [Am]kicked when you're [F]down, to feel like [C]you've been pushed [G]around
To be [Am]on the edge of [F]breaking down, when [C]no one's there to [G]save you
[Dm]No you don't know what its like
[F] Welcome to my [C]life

Do you wanna be somebody else?
Are you sick of being so left out?
Are you desperate to find something more,
before your life is over?
Are you stuck inside a world you hate?
Are you sick of everyone around?
With the big fake smiles and stupid lies,
While deep inside your bleeding

® 

No one ever lies straight to your face
And [Am]no one ever stabs you in the back
[F]You might think I'm happy
But I'm [C]not gonna be [G]okay
[F]Everybody always gave you what you wanted
You [Am]never had to work it was always there
You [F]don't know what it's like what it's [G]like..

To be hurt, to feel lost, to be left out in the dark
To be kicked when you're down, to feel like you've been pushed around
To be on the edge of breaking down, when no ones there to save you
No you don't know what its like, what its like
®
Welcome to my life
Welcome to my [C G]life
Welcome to my [C]life..

